### 2016-07-13 version0.0/paper1.tex
adding prelude to into. section
finishing intro0.0
finishing edits on intro

\chapter[Star formation laws in M31]{Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}

@@

%\subsection{IR and sub mm Data}
Calculations of the SFR using the total infrared emission requires observations at 8, 24, 70, and 160~\um, made
with the {\em Spitzer} \citep{Werner04} and {\em Herschel} \citep{Pilbratt10}  space telescopes. 
Observations with the Infrared Array Camera (IRAC; \citep{Fazio04}) are made in four channels (3.6, 4.5, 5.8, and 8~\um); IRAC observations of M31 were obtained by \citet{Barmby06}, covering a region $3\degr.7 \times 1\degr.6$. 
The Multiband Imaging Photometer for \Spitzer (MIPS) observed M31 at 24, 70, and 160 \um and covered a region $\sim 3\degr \times 1\degr$ \citep{Gordon06}. {\em Herschel} observations of M31 were made with with PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10}  at 100 and 160~\um and SPIRE  \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} 
at 250, 350, and 500~\um, covering a region  $\sim 5\degr.5 \times 2\degr.5$ \citep{Fritz12}.
The IRAC 8, MIPS 24, MIPS 70, and PACS 160 images were used to calculate M31's total infrared emission. 
The IRAC 3.6~\um band image was used to calculate the stellar mass.

%\subsection{Radio Emission}
Gas densities in galaxies are derived from observations at millimetre and centimetre radio wavelengths.
Emission from the $^{12}$CO (J:$1\rightarrow0$) line observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of M31's interstellar medium. This map covers a $2\degr \times 0\degr.5$ region with an angular resolution of $23\arcsec$ and has the smallest coverage of the galaxy among the maps we used in this paper. In this study, we also used a 21-cm emission map of the atomic gas (H\,{\sc I}) in M31 from \citet{Chemin09}. This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a $5\degr.1 \times 1\degr.5$ region with an angular resolution of $60\arcsec \times 90\arcsec$.

@@

Our first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \citet{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}. The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction. On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $\la10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the \citet{Kroupa03} IMF as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{\rm obs}+3.89L(24\mu m)],
\end{equation}
\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\rm obs}$ are in erg~s$^{-1}$. L(FUV)$_{\rm obs}$ is the luminosity of the galaxy in the FUV. The subscript "obs" indicates that the FUV emission is not corrected for extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \citet{Leroy08}. We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission. This process results in masking about 3\% of the pixels within a 25 kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR. 
Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map. We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$. The reported uncertainty for the total SFR only considers the values we measured and does not include uncertainties related to the masked pixels.

@@

%=164mm, height=218mm
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../image_paper1/ks_all_density.pdf}
\caption{Results from fitting the Kennicutt-Schmidt law to data from the whole galaxy using the pixel-by-pixel method. The colour represents the density of the pixels, increasing from blue to red. The number of points among the three columns is different due to the different angular resolution of the H\,{\sc I} and H$_2$ maps. Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc (for maps with resolution of 23\arcsec) while each point for which the surface density of H\,{\sc I} or total gas mass is a tracer represents a region of size $\sim$155~pc (for maps with resolution of $60\arcsec \times 90\arcsec$). Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
\label{fig:ks_all}
\end{figure*}

@@

>>>>

\chapter[Star formation laws in M31]{Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}
\label{ch: paper1}

@@

%\subsection{IR and sub mm Data}
Calculations of the SFR using the total infrared emission requires observations at 8, 24, 70, and 160~\um, made
with the {\em Spitzer} \citep{Werner04} and {\em Herschel} \citep{Pilbratt10}  space telescopes. 
Observations with the Infrared Array Camera (IRAC; \citep{Fazio04}) are made in four channels (3.6, 4.5, 5.8, and 8~\um); IRAC observations of M31 were obtained by \citet{Barmby06}, covering a region 3\degr.7$\times $1\degr.6. 
The Multiband Imaging Photometer for \Spitzer (MIPS) observed M31 at 24, 70, and 160 \um and covered a region $\sim 3$\degr $\times$ 1\degr \citep{Gordon06}. {\em Herschel} observations of M31 were made with with PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10}  at 100 and 160~\um and SPIRE  \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} 
at 250, 350, and 500~\um, covering a region  $\sim$5\degr.5 $\times$ 2\degr.5~\citep{Fritz12}.
The IRAC 8, MIPS 24, MIPS 70, and PACS 160 images were used to calculate M31's total infrared emission. 
The IRAC 3.6~\um band image was used to calculate the stellar mass.

%\subsection{Radio Emission}
Gas densities in galaxies are derived from observations at millimetre and centimetre radio wavelengths.
Emission from the $^{12}$CO (J:$1\rightarrow0$) line observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of M31's interstellar medium. This map covers a 2\degr $\times$ 0\degr.5 region with an angular resolution of 23\arcsec and has the smallest coverage of the galaxy among the maps we used in this paper. In this study, we also used a 21-cm emission map of the atomic gas (H\,{\sc I}) in M31 from \citet{Chemin09}. This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a 5\degr.1 $\times$ 1\degr.5 region with an angular resolution of 60\arcsec $\times$ 90\arcsec.

@@

Our first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \citet{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}. The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction. On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $\la10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the~\citet{Kroupa03} IMF as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{\rm obs}+3.89L(24\mu m)],
\end{equation}
\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\rm obs}$ are in erg~s$^{-1}$. L(FUV)$_{\rm obs}$ is the luminosity of the galaxy in the FUV. The subscript "obs" indicates that the FUV emission is not corrected for extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \citet{Leroy08}. We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission. This process results in masking about 3\% of the pixels within a 25 kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR. 
Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map. We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$. The reported uncertainty for the total SFR only considers the values we measured and does not include uncertainties related to the masked pixels.

@@

%=164mm, height=218mm
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../image_paper1/ks_all_density.pdf}
\caption{Results from fitting the Kennicutt-Schmidt law to data from the whole galaxy using the pixel-by-pixel method. The colour represents the density of the pixels, increasing from blue to red. The number of points among the three columns is different due to the different angular resolution of the H\,{\sc I} and H$_2$ maps. Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc (for maps with resolution of 23\arcsec) while each point for which the surface density of H\,{\sc I} or total gas mass is a tracer represents a region of size $\sim$155~pc (for maps with resolution of 60\arcsec $\times$ 90\arcsec). Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
\label{fig:ks_all}
\end{figure*}

@@

\addcontentsline{toc}{section}{Bibliography}
\bibliographystyle{apj.bst}
\bibliography{ref_paper1.bib}
